Global land characterisation using land cover fractions at 100 m resolution

### 2021-02-18 article/article.tex
UTF-8 to LaTeX

\author[WURGRS]{Dainius Masiliūnas\corref{ca}}
\ead{dainius.masiliunas@wur.nl}
\cortext[ca]{Corresponding author}

@@

Results showed that the random forest regression model reached the lowest RMSE of 17.3\%. Lowest MAE (7.9\%) and highest overall accuracy (72±2\%) was achieved using random forest regression with our proposed three-model approach and median vote.

>>>>

\author[WURGRS]{Dainius Masili\={u}nas\corref{ca}}
\ead{dainius.masiliunas@wur.nl}
\cortext[ca]{Corresponding author}

@@

Results showed that the random forest regression model reached the lowest RMSE of 17.3\%. Lowest MAE (7.9\%) and highest overall accuracy (72±2\%) was achieved using random forest with our proposed three-model approach and median vote.
